---
title: "24/10 LAB"
format: html
editor: visual
author: "Leopold GROSS"
code-fold: true
---

```{r, message=FALSE, echo=FALSE}

#| echo: false
#| mesage: false

 here::i_am("r-101-grade-analysis.Rproj")
 library(ggplot2)
 library(vroom)
 library(dplyr)
 library(tidyr)
library(here)
library(stringr)

```

## Question 1

```{r, echo=FALSE, message=FALSE}

grades <- vroom(here("grades.csv"))
```

## Question 2

```{r, message=FALSE, echo=FALSE}
grades %>% summarise(min=min(Exam, na.rm = TRUE), max=max(Exam, na.rm = TRUE), mean=mean(Exam, na.rm = TRUE)) %>% knitr::kable()

```

We can take a look at the minimum, maximum and mean grade at the exam.

## Question 3

```{r}
nb_stud_exam<-sum(is.na(grades$Exam))
```

There is a total of `r nb_stud_exam` students who did not pass the test

## Question 4

Here is a distribution of grades at the final exam

```{r, message=FALSE, echo=FALSE}

grades %>% ggplot(aes(x=Exam)) + geom_bar() + xlab("grade") +ylab("number of students")
```
## Question 5

```{r}
grades %>% group_by(Group) %>% summarise(N=n()) %>% knitr::kable()
```

## question 6

```{r}
grades %>% ggplot(aes(x=Group)) + geom_bar()
```

## Question 7

```{r, echo=FALSE, message=FALSE}
ggplot(grades, aes(x = Group, y = Exam)) +
  geom_boxplot(fill = "lightblue", color = "black") +
  labs(title = "Distribution of Exam Grades by Group", x = "Group", y = "Exam Grades")
```
here's an alternative version of the distribution
```{r, echo=FALSE, message=FALSE}

ggplot(grades, aes(x = Group, y = Exam, fill = Group)) +
  geom_violin() +
  labs(title = "Distribution of Exam Grades by Group (Violin Plot)", x = "Group", y = "Exam Grades") 
```

## Question 8

```{r}
missed_exam<- grades|>group_by(Group)|>summarise(Nb_Missed_Exam=sum(is.na(Exam)))
knitr::kable(missed_exam)
```
## Question 9
```{r}
ggplot(missed_exam,aes(x=Group,y=Nb_Missed_Exam))+
  geom_col()+
  labs(title="Missing students to the final exam by group", x="Groups",y="Number of missing students")
  
```

## Question 10
```{r}
longformat<-pivot_longer(grades,cols=c(Exam,starts_with("MCQ"),starts_with("Online")),names_to="name",values_to="value")

```
## Question 11
```{r}
missing_grades<-longformat %>% group_by(Id) %>% summarise(total_missing=sum(is.na(value)))
knitr::kable(missing_grades)
```
here is the number of missiing grades per student.

## Question 12
```{r}
ggplot(data = missing_grades, aes(x = Id, y = total_missing)) +
  geom_bar(stat = "identity", fill = "orange") +
  labs(
    title = "Distribution of Missing Grades per Student",
    x = "Student ID",
    y = "Number of Missing Grades"
  ) 
```
## Question 13
```{r}
missing_stud_per_grp<-longformat %>%group_by(Group)%>%filter(name=="Exam")|>summarise(num_missing=sum(is.na(value)))
knitr::kable(missing_stud_per_grp)
```
## Question 14
```{r}
online_mcq_data<-longformat %>% filter(str_starts(name,"Online"))
missing_online_grade<-online_mcq_data %>% group_by(Id) %>% summarise(num_missing=sum(is.na(value)))
knitr::kable(missing_online_grade)
```

Here is the number of missing grades of each students when it comes to online tests.

## Question 15

```{r}
result<-grades %>% rowwise()%>% mutate(missingonlinegrades=sum(is.na(c_across(starts_with("Online")))))

ggplot(result,aes(x=Exam))+
  geom_histogram(binwidth=1,fill="blue",color="black")+
  facet_wrap(~missingonlinegrades)
```
## Question 16
```{r}
missed_mcq <- longformat %>% group_by(Id) %>% summarise(Missed = any(is.na(value) & str_starts(name, "MCQ_"))) 
knitr::kable(missed_mcq)
```

## Question 17
```{r}
group_missed_percentage <- missed_mcq %>%
  inner_join(grades %>% select(Id, Group), by = "Id") %>%
  group_by(Group) %>%
  summarise(P_missed = mean(Missed) * 100)

knitr::kable(group_missed_percentage)

```
## Question 18
```{r}
average_exam_grade <- grades %>% group_by(Group) %>% summarise(Average_Exam_Grade = mean(Exam, na.rm = TRUE))

  merged_tables <- inner_join(average_exam_grade, group_missed_percentage, by = "Group")

ggplot(merged_tables, aes(x = P_missed, y = Average_Exam_Grade)) +
  geom_point() +
  labs( x = "missed MCQ",y = "Average grade" )
```

